A Practical Optional Type System for Clojure

### 2012-10-24 dissertation/paper.tex
Fix incomplete references
Thanks

Last November I attended my first conference, Clojure Conj 2011 (Raleigh, NC),
where I delivered a talk on logic programming with Clojure and met some of my programming heroes.
A week later my supervisor Rowan Davies invited me to visit Carnegie-Mellon University
where he was working on his PhD project. Most memorably, I was invited to a meeting between
Rowan and his PhD supervisor Frank Pfenning, which was a great thrill.

@@

Finally, thanks to my family, friends and to my girlfriend Tamara for your love and support.

>>>>

Last November I attended my first conference, Clojure Conj 2011 (Raleigh, NC),
where I delivered a talk on logic programming with Clojure and met some of my programming heroes.
A week later my supervisor Rowan Davies invited me to visit Carnegie Mellon University
where he was working on his PhD project. Most memorably, I was invited to a meeting between
Rowan and his PhD supervisor Frank Pfenning, which was a great thrill.

@@

Finally, thanks to my family, friends and to my girlfriend Tamara, each for your love and support.
